Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 method.tex
Demoted some subsubsections to subsections
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@850 ccdd05d5-56c1-461a-bf98-85f6876523b4

\subsubsection{Selectively reducing the sample rate of the data and template waveforms}

@@

\subsubsection{Reducing the number of filters with the singular value
decomposition}

>>>>

\subsection{Selectively reducing the sample rate of the data and template waveforms}

@@

\subsection{Reducing the number of filters with the singular value
decomposition}
